Coupling the Level Set Method to Moments and Particles for Computing N-phase flows with phase change.

### 2024-05-20 CouplingLevelSetToMomentsAndParticles_paper/CouplingLevelSetToMomentsAndParticles.tex
relaxation factor

\newpage
\par\noindent
Ghost Fluid Method for surface tension \cite{kang2000boundary}:
\begin{eqnarray*}
\frac{p_{I,L}-p_{L}}{\rho_{L}\theta_{L}\Delta x}=
\frac{p_{R}-p_{I,R}}{\rho_{R}\theta_{R}\Delta x}
\end{eqnarray*}

% gas on left  liquid on right  normal=+1 (liquid level set) \kappa>0
\begin{eqnarray*}
p_{I,R}-p_{I,L}=-\sigma\kappa 
\end{eqnarray*}

@@

\begin{eqnarray*}
\frac{p_{R}\rho_{f}-p_{I,R}\rho_{f}}{\rho_{f}\rho_{R}\theta_{R}\Delta x}=
\end{eqnarray*}
\begin{eqnarray*}
\frac{p_{R}\rho_{R}\theta_{R}-p_{L}\rho_{R}\theta_{R}+
 \sigma\kappa\rho_{R}\theta_{R}}{\rho_{f}\rho_{R}\theta_{R}\Delta x}=
\end{eqnarray*}
\begin{eqnarray*}
\frac{p_{R}-p_{L}}{\rho_{f}\Delta x}+\sigma\kappa\frac{1}{\rho_{f}\Delta x}
\end{eqnarray*}
Assume
\begin{eqnarray*}
|\kappa|<\frac{1}{\Delta x},
\end{eqnarray*}
then we want:
\begin{eqnarray*}
\left(\Delta t \sigma\frac{1}{\rho_{f}\Delta x^{2}}\right)\Delta t \le 
\frac{1}{2}\Delta x
\end{eqnarray*}
\begin{eqnarray*}
\Delta t \le \Delta x^{3/2} \sqrt{\frac{\rho_{f}}{2\sigma}}
\end{eqnarray*}

@@

\par\noindent
Slope reconstruction using level set function, particles, centroid and
volume fraction:
\begin{eqnarray*}
 \phi(\vec{x})=\vec{n}\cdot(\vec{x}-\vec{x}_{0})+b
\end{eqnarray*}
\begin{eqnarray*}
(\vec{n},b)=\mbox{argmin}
 \sum_{ijk}\delta(||\vec{x}_{ijk}-\vec{x}^{c}||)
 (\phi(\vec{x}_{ijk})-\phi_{ijk})^{2}+
 \sum_{p}\delta(||\vec{x}_{p}-\vec{x}^{c}||)
 (\phi(\vec{x}_{p})-\phi_{p})^{2}
\end{eqnarray*}
Replace the least squares $b$ with that which is derived from the 
reference volume fraction $F^{ref}$:
\begin{eqnarray*}
\mbox{VOLFRAC}(\vec{n},b^{ref})=\mbox{VOLFRAC}^{ref}
\end{eqnarray*}

>>>>

\newpage
\par\noindent
Ghost Fluid Method for surface tension \cite{kang2000boundary}:
\begin{eqnarray*}
\frac{p_{I,L}-p_{L}}{\rho_{L}\theta_{L}\Delta x}=
\frac{p_{R}-p_{I,R}}{\rho_{R}\theta_{R}\Delta x}
\end{eqnarray*}
\par\noindent
Derivation for the simple case when there is
gas on the left, liquid on the right, the normal pointing from gas to liquid is
$\vec{n}=(1,0,0)$ and $\kappa>0$:
\begin{eqnarray*}
p_{I,R}-p_{I,L}=-\sigma\kappa 
\end{eqnarray*}

@@

\begin{eqnarray*}
\frac{p_{R}\rho_{f}-p_{I,R}\rho_{f}}{\rho_{f}\rho_{R}\theta_{R}\Delta x}=
\end{eqnarray*}
\begin{eqnarray*}
\frac{p_{R}\rho_{R}\theta_{R}-p_{L}\rho_{R}\theta_{R}+
 \sigma\kappa\rho_{R}\theta_{R}}{\rho_{f}\rho_{R}\theta_{R}\Delta x}=
\end{eqnarray*}
\begin{eqnarray*}
\frac{p_{R}-p_{L}}{\rho_{f}\Delta x}+\sigma\kappa\frac{1}{\rho_{f}\Delta x}
\end{eqnarray*}
Assume
\begin{eqnarray*}
|\kappa|<\frac{1}{\Delta x},
\end{eqnarray*}
then we want:
\begin{eqnarray}
\left(\Delta t \sigma\frac{1}{\rho_{f}\Delta x^{2}}\right)\Delta t \le 
	\frac{1}{2}\Delta x \label{tensioncfl}
\end{eqnarray}
Rationale for $\Delta x/2$ instead of $\Delta x$.  We enforce two constraints:
\begin{enumerate}
	\item $U\Delta t<\Delta x/2$
	\item $(\Delta t\sigma\kappa\nabla H/\rho)\Delta t<\Delta x/2$
\end{enumerate}
Therefore,
\begin{eqnarray*}
 \left(U+\Delta t\sigma\kappa\nabla H/\rho\right)\Delta t<\Delta x
\end{eqnarray*}
So, from (\ref{tensioncfl}),
\begin{eqnarray*}
\Delta t \le \Delta x^{3/2} \sqrt{\frac{\rho_{f}}{2\sigma}}
\end{eqnarray*}
Consistent algorithm that is not conservative, but much more lenient time step
constraint:
\begin{enumerate}
	\item Let 
		$\rho_{cutoff}=\max(\rho_{L},\rho_{R})/\mbox{RelaxationFactor}$
	\item if the level set function changes sign across a face; i.e. 
		$\phi_{left}$ and $\phi_{right}$ have opposite signs then
		$\rho_{f}$ replaced by $\min(\rho_{f},\rho_{cutoff})$.
\end{enumerate}

@@

\par\noindent
Slope reconstruction using level set function, particles, centroid and
volume fraction:
\begin{eqnarray*}
 \phi(\vec{x})=\vec{n}\cdot(\vec{x}-\vec{x}_{0})+b
\end{eqnarray*}
\begin{eqnarray*}
(\vec{n},b)=\mbox{argmin}
 \sum_{ijk}\delta_{4\Delta x}(||\vec{x}_{ijk}-\vec{x}^{c}||)
 (\phi(\vec{x}_{ijk})-\phi_{ijk})^{2}+
 \sum_{p}\delta_{4\Delta x}(||\vec{x}_{p}-\vec{x}^{c}||)
 (\phi(\vec{x}_{p})-\phi_{p})^{2}
\end{eqnarray*}
\begin{eqnarray*}
	\delta_{\epsilon}(x)=\left\{ \begin{array}{cc}
		0 & |x|>\epsilon \\
		\frac{1+\cos(\pi x/\epsilon)}{2\epsilon}
	\end{array} \right.
\end{eqnarray*}
Replace the least squares $b$ with that which is derived from the 
reference volume fraction $F^{ref}$:
\begin{eqnarray*}
\mbox{VOLFRAC}(\vec{n},b^{ref})=\mbox{VOLFRAC}^{ref}
\end{eqnarray*}
